## packages

```{r}
library(tidyverse)
library(rvest)
library(curl)
library(splashr)
```

## setup

```{r}
killall_splash()
splash_svr=start_splash() # seems not to need sudo
Sys.sleep(10)
splash('localhost') %>% splash_active() # this takes a moment to get going. check it again.
```

## grab xscores

```{r}
my_url="http://old.xscores.com/soccer/soccer.jsp?menu3=5"
splash('localhost') %>% render_html(my_url,wait=3, timeout = 60) -> html # this is where safely/possibly goes
```

## examine

```{r}
html %>% html_table(fill=T) %>% .[[5]] -> scores
scores
```

have I lost the headings or were they never there?

```{r}
html %>% html_nodes("tr")
```

they weren't there but are hidden in class

```{r}
html %>% html_nodes("tr") %>% html_attr("class") %>% enframe() %>% separate_rows(value, sep="#") -> thing
thing 
```

```{r}
thing %>% count(name) %>% filter(n==5) -> full_rows
thing %>% 
  left_join(full_rows) %>% 
  filter(n==5) %>% # 1850 rows, 370 matches
  mutate(col_name=gl(5, 1, 1850, labels=c("country", "id", "abb", "key", "what"))) %>% 
  spread(col_name, value)

```

can I do some nested like thing?

(ref)[https://stackoverflow.com/a/39048255/4594336]


```{r}
html %>% html_nodes("tr") -> rows
rows %>% html_attr("class") %>% enframe() -> classes
rows %>% map(~html_nodes(.,"td")) %>% map(~html_text(.)) -> table_data
nrow(classes)
classes
length(table_data)
```


```{r}
table_data[[338]] 
```

write a function returning from this a one-row data frame of stuff I want

```{r}
table_data[[338]] %>% .[14:17] %>% str_c(collapse=":")
one_row=function(v) {
  tibble(stat=v[2], mins=v[3], lg=v[5], team1=v[6],
         pos1=v[7], team2=v[10], pos2=v[11], ht=v[14], 
         ft=v[15], et=v[16], pens=v[17], scores=str_c(v[14:17], collapse=":"))
}

```

grab stuff from classes that I want too and bind cols

```{r}
classes %>% as_tibble() %>% 
  separate(value, into=c("country", "id", "abb", "key", "league"), sep="#", convert=T) %>% 
  mutate(level=id %/% 10) %>% 
  mutate(what=str_c(country, ": ", league, " (", level, ")")) %>% 
  select(what) -> whats
table_data %>% map_df(~one_row(.)) -> scores
scores %>% bind_cols(whats) %>% filter(!is.na(what)) %>% 
  select(what, stat, mins, team1, pos1, team2, pos2, ft, scores)
```

that looks good. 

now, write a function that makes all that happen from html. Or, better, a string of small functions.



