---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# livescore

Following world soccer games, live.

## Preparation

- Install Docker.
- In R Studio the first time, run this:

```{r, eval=F}
library(splashr)
install_splash()
```

The `install_splash` only needs to be run once.

## Setup

In R Studio, open 0-xscores2.R. Click on Jobs (in R Studio 1.2), and Start Local Job. This runs this script in the background; it connects to xscores every 2 minutes or so and downloads the latest scores. Give it a couple of minutes to get going.

## To check scores

Open xscores-sep.Rmd. Run this entire notebook (ctrl-shift-R). This will display the complete score history of all the games whose status has changed since the last time you ran this (that is, game started, game ended, game reached halftime, goal scored; also gone into extra time/penalties if applicable). Games are sorted by league abbreviation (eg. A for Italian Serie A, EPL for English Premier).