---
title: "live scores from soccerway"
output: html_notebook
---

## packages

```{r}
library(tidyverse)
library(rvest)
library(lubridate)
source("scoresway-live-functions.R")
goback=0
```

## get games from scoresway

```{r}
base="https://www.soccerway.com"
games <- readRDS("~/teaching/scoresway/rds/games.rds")
now <- Sys.time()
games %>% 
  select(match, comp, time_stamp) %>% 
  mutate(hours_ago=(now-time_stamp)/dhours(1)) %>% 
  filter(between(hours_ago, -goback, 3 )) %>% 
  select(match, comp) -> matches
matches
```

These are the games happening now (or recently finished). Idea: modify the 0 or 3 to be hours since last look, to include games that might have changed since last look.

## pulling game and extracting info



start from "today" page: ends with r, 5 digits and a slash

```{r}
comp_urls=get_today()
```

so, which competition URLs do I want?

```{r}
comps_now <- get_comps_now(matches, comp_urls)
comps_now
```

get the games from a competition that are on the original match list and info for them

```{r}
```

and now do this for all the leagues on my list (this looks shaky)

```{r}
d_old=d
d_old_time=d_time
d_time=Sys.time()
nrow(comps_now)
comps_now %>% mutate(today_games=map(comp, ~get_all_comp_games(matches, comps_now, .))) %>%
  unnest(cols = c(today_games), names_repair="unique") %>% 
  select(value, match, t1, t2, score, mins) -> d
print("Done.")
View(d)
View(d_old)

```

compare d_old and d
maybe write function to take snapshot (though run all does it for now)


```{r}
d_old %>% full_join(d, by="match") %>% 
  select(value=value.x, t1=t1.x, t2=t2.x, score1=score.x, score2=score.y, mins1=mins.x, mins2=mins.y) %>% 
  mutate(event=case_when(
    mins1!="XX" & mins2=="XX" ~ "finished",
    mins1=="XX" & mins2!="XX" ~ "started",
    score1 != score2 ~ "goal",
    TRUE ~ "none"
  )) %>% 
  filter(event != "none") %>% 
  arrange(value) %>% 
  separate(value, into=c("blank", "type", "country", "league"), sep="/") %>% 
  View("Changes")
```

