---
title: "Xscores tables"
output: html_notebook
---

## Packages

```{r}
library(tidyverse)
library(lubridate)
last_seen=ifelse(exists("last_seen"),last_seen,0)
```

set up interval between gets

```{r}
interval=3
saveRDS(list(interval=interval), "opts.rds")
readRDS("opts.rds")
```


###################### instructions

use splashr::killall_splash() in console to kill any previous splash containers
use docker run in terminal to start splash process
run 0-xscores2.R as local job


#######################



Arrange file names as a list of dates and times, and work out how long since. What I do later is to keep track of last observation time and keep only ones since then (or that minus something).
  
```{r}
tz="America/Toronto"
list.files(pattern="2*.rds") %>% enframe(name="seq", value="file") %>% 
  mutate(dt=ymd_hms(file, tz=tz)) %>% 
  drop_na() %>% 
  mutate(since=(Sys.time()-dt)/dminutes(1)) -> d
```

```{r}
d
```

now read in the table in the file in `file` into a list-col and process

```{r}
d %>% mutate(tab=map(file,~readRDS(.))) %>% unnest(tab) %>% select(-c(seq, file, since)) %>% 
  mutate(key=str_c(team1, team2, sep=" v ")) %>% 
  arrange(key, dt) %>% filter(ft!="-") %>% 
  filter(ft!="FINISHED GAMES") %>% 
  filter(key !="Home v Away") -> d1
```




make a composite of scores. Can calculate surprise here. ft (split), pos1, pos2, half a goal for HA.

```{r}
d1 %>%  
  mutate(prev_score=lag(scores)) %>% 
  mutate(prev_stat=lag(stat)) %>% 
  mutate(prev_key=lag(key)) %>% 
  mutate(row=row_number()) %>% 
  separate(ft,into=c("s1","s2"),sep="-", remove=F, convert=T) %>% 
  mutate(surprise=-(s1-s2-0.5)*(as.numeric(pos1)-as.numeric(pos2))) -> d2
```




display lines where score is different but game is same (this will need gradual working on)

show:

1 first line for a game (previous key is different)
2 a line where the previous score is different
3 a line where stat=Fin and the previous stat is not
4 very first line

```{r}
d2 %>% 
  mutate(cond1=(key != prev_key),
         cond2=(prev_score != scores),
         cond3=(stat=="Fin") & (prev_stat!="Fin"),
         cond4=(row==1)) %>% 
  filter(cond1 | cond2 | cond3 | cond4) -> d3
```

Is that everything? (Will investigate.)

`d3` contains all the lines that are showable:

```{r}
d3
```



Find latest time for each game:

```{r}
d3 %>% group_by(key) %>% summarize(latest=max(dt), count=n()) %>% arrange(latest) -> d4
```

```{r}
d4 %>% arrange(desc(latest))
```

casification

```{r}
not_words=c(
  "Fc", "Fk", "Ff", "Spal", "If", "Fsv", "Lask", "Gd", "Bk", "Sc", "Us", "As", "Hb", "b", "Ii", "Uil",
  "Cd", "Ud", "Ue", "Ucam", "Bb", "Hifk", "Ifk", "Kups", "Rops", "Fs", "Tp", "Mfm", "Cska", "Cf", "Up", "Scd",
  "Sd", "Ik", "if", "Aif", "Ec", "Mte", "Vse", "Lu", "Bsk", "Vps", "Eto", "Bate", "Nsi", "Ab", "Cfr", "Cs", 
"Ldu", "Rs", "Kr", "Fbc", "Dc", "Csd", "Ktp", "Eif", "Pec", "Psv", "Vvv", "Afc", "Ca", "Acs", "Uta", "Hjk", "Kvc",
"Nk", "Hnk", "Ado", "Nac", "Ia", "Fh", "Ka", "Ofk", "Kpv", "Tpv", "Ac", "Gks", "Bw", "Sv", "Csm", "Fcsb", "Estac",
"Fci", "Bfc", "Ucd", "Ukm", "Svg", "Sv", "Vfb", "Vfl", "Tsv", "Ssv", "Fv", "Ak", "Tsg", "Kcb", "Kfc", "Sjk", "Sg", "Csms", "Js",
"Uitm", "Lks", "Ns", "Nd", "Kf", "Mtk", "Tc", "Tb", "Ki", "Ibv", "Psm", "Osk", "Hk", "Aik", "Gif", "Msk", "Mfk", "Skf", "Zp",
"Crb", "Bsu", "Jk", "Pfc", "Shb", "Scr", "Pss", "Pkns", "Ptt", "Cp", "Rb", "Bsc", "Abc", "Okc", "Rgv", "Sipg", "R&f", "Agmk", "Eb",
"Skn", "Csa", "Sk", "Wsg", "Ksv", "Gais", "Tps", "Mypa", "Ons", "Djk", "Pknp", "Qpr", "Nec", "Slc", "Pdrm", "Tsc", "Msv", "Zfc",
"Az", "Aek", "Paok", "Kcca", "Kmc", "Ska", "Ts", "Njs", "Ae", "Mvv", "Vsg", "Psni", "Oo", "Sku", "Vfr", "Kv", "Oh", "Ps", "Dpmm", "Jdr",
"d", "Wit", "Kfum", "Ad", "Asc", "Pae", "Rw", "Ao", "Utc", "Ld", "Ums", "Ofi", "Ct", "Sad", "Bfa", "Fa", "Te",
"Fif"
)
sort(not_words)
upify=tibble(from=str_c("\\b", not_words, "\\b"),
             to=toupper(not_words)
)
changes=upify$to
names(changes)=upify$from
casify=function(x, changes) {
  y=tools::toTitleCase(tolower(x))
  str_replace_all(y, changes)
}
```




look up latest times, omit ones for which count is too big

```{r}
d3 %>% left_join(d4) %>% arrange(what, key, dt) %>% 
  filter(count<50) %>% 
  select(2:8, ft, surprise, scores, dt, latest) %>% 
  filter(latest>last_seen) -> d5
d5 %>% mutate_at(vars(starts_with("team")), ~casify(.,changes))  -> d6
d6 %>% mutate(what_x=ifelse(row_number()>1 & what==lag(what), "", what)) %>% 
  mutate(team1_x=ifelse(row_number()>1 & team1==lag(team1), "", team1)) %>% 
  mutate(team2_x=ifelse(row_number()>1 & team2==lag(team2), "", team2)) -> d6 # not quite: make copies and select cols when displaying
d6 %>% select(what=what_x, stat=stat, mins=mins,
              team1=team1_x, pos1=pos1,
              team2=team2_x, pos2=pos2,
              ft:latest) %>% View("Scores")
```

leagues I care about


```{r}
i_care <- c("ENGLAND: CHAMPIONSHIP (21)", "ENGLAND: PREMIER LEAGUE (11)", "FRANCE: LIGUE 1 (10)", "GERMANY: BUNDESLIGA (11)", "GREECE: SUPER LEAGUE 1 (11)", 
            "ITALY: SERIE A (11)", "SCOTLAND: SCOTTISH PREMIERSHIP (11)", "SPAIN: PRIMERA DIVISION (11)",
            "SWEDEN: ALLSVENSKAN (11)",
            "EUROPE (UEFA): UEFA CHAMPIONS LEAGUE (16)") # add europa league, Sweden when it starts
d6 %>% filter(what %in% i_care) %>%
  select(what=what_x, stat=stat, mins=mins,
              team1=team1_x, pos1=pos1,
              team2=team2_x, pos2=pos2,
              ft:latest) %>%
  View("PTF")
```


games with a team in the top 3

```{r}
d6 %>% filter(as.numeric(pos1)<=3 | as.numeric(pos2)<=3) %>% 
   mutate(what_x=ifelse(row_number()>1 & what==lag(what), "", what)) %>% 
  mutate(team1_x=ifelse(row_number()>1 & team1==lag(team1), "", team1)) %>% 
  mutate(team2_x=ifelse(row_number()>1 & team2==lag(team2), "", team2)) %>% 
    select(what=what_x, stat=stat, mins=mins,
              team1=team1_x, pos1=pos1,
              team2=team2_x, pos2=pos2,
              ft:latest) %>%
View("top3")
```

teams I like


```{r}
my_faves=c("Reading", "Torquay", "Dover", "Gillingham", "Aston Villa", "Coventry", "FC Kaiserslautern", "Montrose", "Halmstad", "Slask Wroclaw", "Blyth Spartans",
           "Exeter", "Plymouth", "Truro", "Vancouver Whitecaps", "Toronto FC", "Deportivo La Coruna", "Real Oviedo", "Rot-Weiss Essen", "Sampdoria", "BATE Borisov")
d6 %>% filter(team1 %in% my_faves | team2 %in% my_faves) %>% 
    select(what=what_x, stat=stat, mins=mins,
              team1=team1_x, pos1=pos1,
              team2=team2_x, pos2=pos2,
              ft:latest) %>%
  View("faves")
```


do this last, for next time

```{r}
(d4 %>% summarize(the_last=max(latest)) %>% pull(the_last) -> last_seen)
```
