---
title: "Xscores tables"
output: html_notebook
---

## Packages

```{r}
library(tidyverse)
library(lubridate)
last_seen=ifelse(exists("last_seen"),last_seen,0)
```





Arrange file names as a list of dates and times, and work out how long since. What I do later is to keep track of last observation time and keep only ones since then (or that minus something).

```{r}
tz="America/Toronto"
list.files(pattern="2*.rds") %>% enframe(name="seq", value="file") %>% 
  mutate(dt=ymd_hms(file, tz=tz)) %>% mutate(since=(Sys.time()-dt)/dminutes(1)) -> d
```

```{r}
d
```

now read in the table in the file in `file` into a list-col and process

```{r}
d %>% mutate(tab=map(file,~readRDS(.))) %>% unnest(tab) %>% select(-c(seq, file, since)) %>% 
  mutate(key=str_c(team1, team2, sep=" v ")) %>% 
  arrange(key, dt) %>% filter(ft!="-") %>% 
  filter(ft!="FINISHED GAMES") %>% 
  filter(key !="Home v Away") -> d1
```



make a composite of scores. Can calculate surprise here. ft (split), pos1, pos2, half a goal for HA.

```{r}
d1 %>% mutate(all_scores=str_c(ht,ft,et,pens, sep=":")) %>% 
  mutate(prev_score=lag(all_scores)) %>% 
  mutate(prev_stat=lag(stat)) %>% 
  mutate(prev_key=lag(key)) %>% 
  mutate(row=row_number()) %>% 
  separate(ft,into=c("s1","s2"),sep="-", remove=F, convert=T) %>% 
  mutate(surprise=-(s1-s2-0.5)*(as.numeric(pos1)-as.numeric(pos2))) -> d2
```

display lines where score is different but game is same (this will need gradual working on)

show:

1 first line for a game (previous key is different)
2 a line where the previous score is different
3 a line where stat=Fin and the previous stat is not
4 very first line

```{r}
d2 %>% 
  mutate(cond1=(key != prev_key),
         cond2=(prev_score != all_scores),
         cond3=(stat=="Fin") & (prev_stat!="Fin"),
         cond4=(row==1)) %>% 
  filter(cond1 | cond2 | cond3 | cond4) -> d3
```

Is that everything? (Will investigate.)

`d3` contains all the lines that are showable:

```{r}
d3
```



Find latest time for each game:

```{r}
d3 %>% group_by(key) %>% summarize(latest=max(dt), count=n()) %>% arrange(latest) -> d4
```

```{r}
d4 %>% arrange(desc(latest))
```



look up latest times, omit ones for which count is too big

```{r}
d3 %>% left_join(d4) %>% arrange(lg, key, dt) %>% 
  filter(count<50) %>% 
  select(2:8, ft, surprise, all_scores, dt, latest) %>% 
  filter(latest>last_seen) %>% 
  View("Scores")
```


do this last, for next time

```{r}
(d4 %>% summarize(the_last=max(latest)) %>% pull(the_last) -> last_seen)
```

